`flippant` -- An `R` package for the automated  analysis of dithionite scramblase

### 2015-09-19 inst/manuscript/manuscript.rmd
Header reformating;

---
title: "`flippant` -- An `R` package for the automated  analysis of dithionite 
  scramblase assays"
author: "Johannes Graumann ^†,^*, Birgit Ploier ^‡^, Richard J. Cotton ^†^,
  Mike A. Goren ^‡^ and Anant K. Menon ^‡^"
date: "September 16, 2015"
output: 
#  word_document
  pdf_document:
    fig_caption: yes
bibliography: flippant.bib
csl: bioinformatics.csl
---

>>>>

---
title: '`flippant` -- An `R` package for the automated  analysis of dithionite scramblase
  assays'
author: Johannes Graumann ^†,^*, Birgit Ploier ^‡^, Richard J. Cotton ^†^, Mike A.
  Goren ^‡^ and Anant K. Menon ^‡^
date: "September 19, 2015"
output:
#  word_document
  pdf_document:
    fig_caption: yes
csl: bioinformatics.csl
bibliography: flippant.bib
---
